Improving reproducibility of scientific software using Nix/NixOS: A case study on preCICE adapters and solvers

### 2023-11-04 paper/paper.tex
paper: Explain why preCICE is a good fit for the case study

Conducting a large scale research on building scientific codes reproducibly is quite infeasible due to how many different software there is.
Therefore, we conduct a case study, focusing on preCICE\cite{preCICEv2}, its adapters and solvers.
One of the goals of the case study is to get a first hand experience and estimate on the complexity and possible challenges when packaging scientific software.
Also, consistent portability of building the software on three different systems is verified.

>>>>

Conducting a large scale research on building scientific codes reproducibly is quite infeasible due to how many different software there is.
Therefore, we conduct a case study, focusing on preCICE\cite{preCICEv2}, its adapters and solvers.
One of the goals of the case study is to get a first hand experience and estimate on the complexity and possible challenges when packaging scientific software.
Also, consistent portability of building the software on three different systems is verified.
preCICE is a well fit for such a case study, as its official adapters and solvers vary in their programming languages, project sizes and other factors, providing a quite manifold set of scientific simulation software while still being able to verify if the software is still correct by running preCICE simulations across several different solver binaries.
